---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggsano

<!-- badges: start -->
<!-- badges: end -->

The goal of ggsano is to uniform the use of colours within the institue Sciensano. The ggsano package is open-source and can be downloaded by everyone. Currently the package only includes a discrete and continuous color palette, but regular updates are planned.

## Installation

Since ggsano is not available on [CRAN](https://CRAN.R-project.org), you can download  the development version from [GitHub](https://github.com/) by executing the following code:

``` r
# install.packages("devtools")
devtools::install_github("rdpauw/ggsano")
```
## Example

This is are the standard discrete colours included in the ggsano package:

```{r example}
library(ggsano)
library(scales)
show_col(pal_sciensano()(12))
```

You can specify the colours in each row by specifying the `name` argument in the functions

```{r cars}
show_col(pal_sciensano(name = "yellow")(4))
```

